Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-11 paper/paper.tex
comment out abstract

\begin{abstract}
The timbre of a sound is an important factor in determining its identity and source.
One successful means of exploring the timbre space has been the construction of computational models to analyze datasets of musical instrument recordings.
However, these datasets have typically only included a limited set of instruments played with standard playing techniques, limiting the timbral range.
For these datasets, models based on static spectral descriptors, such as mel-frequency cepstral coefficients (MFCCs), have enjoyed excellent performance.
However, with richer datasets containing a wider array of instruments played with a variety of playing techniques, more sophisticated models which incorporate dynamic large-scale signal structure are needed.
To this end, we propose a simple but rich model based on joint time--frequency scattering transforms followed by a linear mapping.
The linear part is learned from human similarity judgments obtained in a crowdsourced free sorting task, so the resulting descriptor provides a perceptually motivated characterization of timbre.
We show that this proposed computational model accurately reproduces the human similarity judgments to $99\%$ accuracy.
In addition, we perform an ablation study demonstrating the necessity of various components in this model.
\end{abstract}

>>>>

\begin{abstract}

\end{abstract}

%\begin{abstract}
%The timbre of a sound is an important factor in determining its identity and source.
%One successful means of exploring the timbre space has been the construction of computational models to analyze datasets of musical instrument recordings.
%However, these datasets have typically only included a limited set of instruments played with standard playing techniques, limiting the timbral range.
%For these datasets, models based on static spectral descriptors, such as mel-frequency cepstral coefficients (MFCCs), have enjoyed excellent performance.
%However, with richer datasets containing a wider array of instruments played with a variety of playing techniques, more sophisticated models which incorporate dynamic large-scale signal structure are needed.
%To this end, we propose a simple but rich model based on joint time--frequency scattering transforms followed by a linear mapping.
%The linear part is learned from human similarity judgments obtained in a crowdsourced free sorting task, so the resulting descriptor provides a perceptually motivated characterization of timbre.
%We show that this proposed computational model accurately reproduces the human similarity judgments to $99\%$ accuracy.
%In addition, we perform an ablation study demonstrating the necessity of various components in this model.
%\end{abstract}
